---
title: "Final Group Project: AirBnB analytics"
date: "12 Oct 2021"
author: "Reading Time: About 8 minutes"
output:
  html_document:
    highlight: zenburn
    theme: flatly
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: show
---


```{r setup, include=FALSE}
# leave this chunk alone
options(knitr.table.format = "html") 
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
  comment = NA, dpi = 300)
```


```{r load-libraries, echo=FALSE}

library(tidyverse) # the usual stuff: dplyr, readr, and other goodies
library(lubridate) # to handle dates
library(GGally) # for correlation-scatter plot matrix
library(ggfortify) # to produce residual diagnostic plots
library(rsample) # to split dataframe in training- & testing sets
library(janitor) # clean_names()
library(broom) # use broom:augment() to get tidy table with regression output, residuals, etc
library(huxtable) # to get summary table of all models produced
library(kableExtra) # for formatting tables
library(moderndive) # for getting regression tables
library(skimr) # for skim
library(mosaic)
library(leaflet) # for interactive HTML maps
library(tidytext)
library(viridis)
library(vroom)
```


```{r load_data, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

# use cache=TRUE so you dont donwload the data everytime you knit

listings <- vroom("http://data.insideairbnb.com/china/beijing/beijing/2021-09-28/data/listings.csv.gz") %>% 
       clean_names()

```


# Exploratory Data Analysis (EDA)

## Looking at the raw values

```{r}
listings %>%
glimpse()
```

## Summary statistics

```{r}
listings %>%
skim()
```

Beijing has 6296 accomodations listed on Airbnb. 

## Data wrangling

Since `price` is a quantitative variable, we need to make sure it is stored as numeric data `num` in the dataframe.

```{r}
listings <- listings %>% 
  mutate(price = parse_number(price))
```

```{r}
typeof(listings$price)
```
```{r}
skim(listings)
```

## Data visualisations

```{r}
# Price (per bedroom) distribution by room type
listings %>%
  filter (!is.na(room_type)) %>%
  mutate ( price_per_bedroom := price/bedrooms ) %>%
  ggplot(aes(x=price_per_bedroom, colour = room_type, alpha=0.4)) +
  geom_histogram() +
  facet_wrap(~room_type)+
  theme_bw() +
  labs (title = "Price Distribution by Room Type")
```

Most of the accommodations available are Entire home/apartment. One very simple reason for that is that sharing rooms in Beijing is quite uncommon, although in this graph we don’t see a huge disparity in the price between these different types of accommodation since all distributions are skewed to the right.


```{r}
# Box plot of price per bedroom by neighbourhoods
listings %>%
  filter (!is.na(neighbourhood_cleansed)) %>%
  mutate ( price_per_bedroom := price/bedrooms ) %>%
ggplot(aes( x = factor(neighbourhood_cleansed))) +
  geom_boxplot(aes(y = price_per_bedroom)) +
  theme( axis.text.x = element_text( angle= 45, hjust = 1)) +  
  scale_y_continuous(limits = c(0,2500)) +
  labs(title = "Box Plot of Price per Bedroom by Neighbourhoods")
```
 
 
``` {r}
listings_1 <- listings %>%
  count(neighbourhood_cleansed)

listings_1 %>% 
  slice_max(order_by = n, n=25) %>% 
  ggplot(aes(x = n, y = fct_reorder(neighbourhood_cleansed, n))) +
  geom_col() +
  labs(
    title = "Neighbourhood ranked by number of listings",
    x = "Number of Listings",
    y = "Neighbourhood")
    ```
    
 
 From the mapping, we have figured out Airbnb listings in Beijing are concentrated in city centre and the northern region around HuaiRou District. The popularity is explained by the convenience to commute in the centre of Beijing and the costly expense for an alternative means of lodging such as hotel. Meanwhile, there are so many scenic spots on the northern side far from city centres (around 2 hours of commuting) and the properties are more appealing with nice views. So tourists prefer to stay at Airbnb if they want to make a visit to these spots.


```{r}
# Correlation matrix of key variables
listings <- listings %>% 
  mutate(log_price := log(price)) # Mutate a new column showing log price
ggpairs(listings, columns = c("log_price",  "accommodates",  "bedrooms", "availability_30", "availability_60", "review_scores_rating", "beds", "number_of_reviews", "minimum_nights"))
```
The highest correlations seem to be between beds, bedrooms and accomodates which is obvious. 
Another interesting but logical correlation is between price and accomodates: a price for an apartment that can accomodate 8 people is logically more expensive than one that accomodates only 2 people.


```{r}
# Box plot of price per bedroom by whether the host is super host
listings %>%
  filter (!is.na(host_is_superhost)) %>%
  mutate ( price_per_bedroom := price/bedrooms ) %>%
ggplot(aes( x = factor(host_is_superhost))) +
  geom_boxplot(aes(y = price_per_bedroom)) +
  theme( axis.text.x = element_text( angle= 45, hjust = 1)) +  
  scale_y_continuous(limits = c(0,2500)) +
  labs(title = "Box Plot of Price per Bedroom by the host")
```
The second one is box plots describing the relationship between prices and whether hosts are super hosts. We can see a small difference, but surprisingly not that big, meaning that being a superhost doesn’t not increase demand for their accommodation that much doesn’t seem to impact the prices. But we’ll try to confirm or deny that later on in the regression analysis.

## Propery types


```{r}
listings <- listings %>%
  mutate(prop_type_simplified = case_when(
    property_type %in% c("Entire villa","Entire residential home", "Farm stay","Private room in farm stay") ~ property_type, 
    TRUE ~ "Other"
  ))
```

The most common property types are Entire VIlla, Entire residnetial home, Farm stay, and Private room in farm stay which is coherent with the first graph we plotted. 


```{r}
listings %>%
  count(property_type, prop_type_simplified) %>%
  arrange(desc(n))        
```        

Airbnb is most commonly used for travel purposes, i.e., as an alternative to traditional hotels. We only want to include  listings in our regression analysis that are intended for travel purposes:

```{r}
listings %>%
  count(minimum_nights)
```
The most common value for minimum_nights is 1.

There are some unusual figures for minimum_nights such as, Airbnb does this to encourage customers to stay longer and spend more money.`

```{r}
listings <- listings %>% 
  filter(minimum_nights <= 4)
```  

# Mapping

```{r, out.width = '80%'}
leaflet(data = filter(listings, minimum_nights <= 4)) %>% 
  addProviderTiles("OpenStreetMap.Mapnik") %>% 
  addCircleMarkers(lng = ~longitude, 
                   lat = ~latitude, 
                   radius = 1, 
                   fillColor = "blue", 
                   fillOpacity = 0.4, 
                   popup = ~listing_url,
                   label = ~property_type)
```

# Regression Analysis

For the target variable $Y$, we will use the cost for two people to stay at an Airbnb location for four (4) nights. 

Create a new variable called `price_4_nights` that uses `price`, and `accomodates` to calculate the total cost for two people to stay at the Airbnb property for 4 nights. This is the variable $Y$ we want to explain.

```{r}
listings <- listings %>% 
  mutate(price_4_nights = (price/accommodates)*2*4) 

#First calculate the unit price then 4 nights then 2 people 


``` 

Use histograms or density plots to examine the distributions of `price_4_nights` and `log(price_4_nights)`. Which variable should you use for the regression model? Why?

```{r}
listings  %>% 
  ggplot()+
  geom_density(aes(x=price_4_nights)) 

listings %>% 
  ggplot()+
  geom_density(aes(x=log(price_4_nights)))

#Density distribution of raw price_4_nights and log(price_4_nights)

``` 
 
Linear regression assumes normal distributions for variables used. Since Log(price_4_nights) fits the normal distribution much better, it should be used instead of price_4_nights variable. 


We fitted a regression model called `model1` with the following explanatory variables: `prop_type_simplified`, `number_of_reviews`, and `review_scores_rating`.

```{r}
model1 <- lm(log(price_4_nights)~prop_type_simplified + number_of_reviews+review_scores_rating,data = listings)

msummary(model1)
``` 
"review_scores_rating" is not a significant indicator of log(price_4_nights) since its P values is 0.27 which is way higher than the 0.05 threshold. 

Since "prop_type_simplified" variable is categorical we need to interpret every type of properties:

- the coefficient of "Other" is not significant (tvalue < 2)
- the "Entire Residential Home" is the base category and it has significant an intercept of 7.7 which implies that this type of property drives the price of the accommodation positively by log(usd) 7.7.
- the property type "Entire Villa" has a significant intercept of 0.14. By adding the intercept of the base category we obtain an intercept of 7.83 which implies that this type of properties drives the price of the accommodation by a relative move of log(usd) 7.83.
- the property type "Farm stay" has a absolute significant intercept of 7.392 which implies that this type of properties drives the price of the accommodation by a relative move of log(usd) 7.39.
- the property type "Private room in a farm stay" has an absolute significant intercept of 6.834 which implies that this type of property drives the price by a relative move of log(usd) 6.834



We want to determine if `room_type` is a significant predictor of the cost for 4 nights, given everything else in the model. . 

```{r}
model2 <- lm(log(price_4_nights)~prop_type_simplified + number_of_reviews+review_scores_rating+ room_type,data = listings)

msummary(model2)
``` 
In the model2, we can observe that room_type is important for both "private room" and "shared room" categories since both of their p value is lower than 0.05.


## Further variables/questions to explore on our own


1. Are the number of `bathrooms`, `bedrooms`, `beds`, or size of the house (`accomodates`) significant predictors of `price_4_nights`? Or might these be co-linear variables?

```{r}
model_3 <- lm(log(price_4_nights)~bedrooms+beds+accommodates,data = listings)

msummary(model_3)

model_3 %>% 
  car::vif(model_3)

``` 
In Beijing data set "bathrooms" variable is empty. Therefore, the analysis is done with "bedrooms", "beds" and "accommodates" variables. All these variables are found significant.

When we investigate VIFs, we see that none of them is higher than 5. Although, "bedrooms" variable is close to 5 with a VIF value of 4.7. So these could potentially be co-linear variables. Therefore, we will add beds and accommodates but not the bedrooms. These variables will be added at the very end to not affect the collinearity in other models. 


1. Do superhosts `(host_is_superhost`) command a pricing premium, after controlling for other variables?

```{r}
model_4 <- lm(log(price_4_nights)~prop_type_simplified + number_of_reviews+review_scores_rating+ room_type+accommodates+host_is_superhost,data = listings)

msummary(model_4)
``` 
Yes, actually it is safe to say super hosts command a price premium since it is a significant variable in the model and its beta is positive.


1. Some hosts allow you to immediately book their listing (`instant_bookable == TRUE`), while a non-trivial proportion don't. After controlling for other variables, is `instant_bookable` a significant predictor of `price_4_nights`?

```{r}
model_5 <- lm(log(price_4_nights)~prop_type_simplified + number_of_reviews+review_scores_rating+ room_type+accommodates+host_is_superhost+instant_bookable,data = listings)

msummary(model_5)

model_5 %>% 
  car::vif(model_5)

``` 

1. For all cities, there are 3 variables that relate to neighbourhoods: `neighbourhood`, `neighbourhood_cleansed`, and `neighbourhood_group_cleansed`. There are typically more than 20 neighbourhoods in each city, and it wouldn't make sense to include them all in your model. Use your city knowledge, or ask someone with city knowledge, and see whether you can group neighbourhoods together so the majority of listings falls in fewer (5-6 max) geographical areas. You would thus need to create a new categorical variabale `neighbourhood_simplified` and determine whether location is a predictor of `price_4_nights`

```{r}

#Reducing the categories for the neighbourhood
listings <- listings %>%
  mutate(neighbourhood_simplified = case_when(
    neighbourhood_cleansed %in% c("怀柔区 / Huairou","延庆县 / Yanqing", "密云县 / Miyun") ~ neighbourhood_cleansed, 
    TRUE ~ "Other"
  ))


# Checking our results
listings %>%
  count(neighbourhood_cleansed, neighbourhood_simplified) %>%
  arrange(desc(n))        

#Creating a 6th model
model_6 <- lm(log(price_4_nights)~prop_type_simplified + number_of_reviews+review_scores_rating+ room_type+accommodates+host_is_superhost+instant_bookable+neighbourhood_simplified,data = listings)

msummary(model_6)

model_6 %>% 
  car::vif(model_6)

  
```
The districts are divided into four according to the knowledge of the group members.  These districts are Huairou, Yanqing, Miyun and others. 

Only Huairou district is significant and it demands a premium on price. This makes sense since Huairou is a high quality district and quite popular on social media. 


1. What is the effect of `avalability_30` or `reviews_per_month` on `price_4_nights`, after we control for other variables?

```{r}
model_7 <- lm(log(price_4_nights)~prop_type_simplified + number_of_reviews+review_scores_rating+ room_type+accommodates+host_is_superhost+instant_bookable+neighbourhood_simplified+availability_30+reviews_per_month,data = listings)

msummary(model_7)

model_7 %>% 
  car::vif(model_7)

``` 


## Diagnostics, collinearity, summary tables

As you keep building your models, it makes sense to:

```{r}
model_final <- lm(log(price_4_nights)~prop_type_simplified + number_of_reviews+ room_type+accommodates+host_is_superhost+instant_bookable+neighbourhood_simplified+availability_30+reviews_per_month+beds,data = listings)
#For the final model review_scores_rating is dropped since it was not a significant variables.
#Beds is added to the model and it doesn't create a significant collinearity problem

msummary(model_final)

model_final %>% 
  car::vif(model_final)

``` 
1. Check the residuals, using `autoplot(model_x)`

```{r}
#Final Model
model_final %>% 
  car::vif(model_final)

autoplot(model_final)
``` 

The residual vs Fitted graph doesn't seem to follow a specific pattern. This means that linearity assumption of regression is checked. The normality graph, while not perfect, seems to fit the normality assumption. 



```{r}
model_final %>% 
  car::vif(model_final) 

``` 

Collinearity is checked at every stage of explanatory variable addition and no significant collinearity problem exists in the data set since all VIF values are significantly below 5. 


1. We created a summary table, using `huxtable`: 

```{r}
library(huxtable)

huxreg(model1, model2, model_4,model_5,model_6,model_7,model_final)

``` 

1. Testing the predictability of our model:

```{r}

filtered_listings <- listings %>% 
  filter(room_type=="Private room") %>% 
  filter(number_of_reviews>= 10) %>% 
  filter(review_scores_rating >= 4.5)  #the data set is filtered. Filtered dataframe has 161 obs.
  
  
predicted <- data.frame(exp(predict(model_final,filtered_listings,interval = "prediction" ))) #cost and intervals are predicted

predicted %>% 
  summarise(avg_price_4_nights = mean(fit),upper=mean(upr),lower=mean(lwr)) #average of fit, upr and lower

predicted$ID <- seq.int(nrow(predicted))
filtered_listings$ID <- seq.int((nrow(filtered_listings)))

filtered_listings_ordered <- filtered_listings %>% 
  left_join(predicted,by="ID") %>% 
  arrange(desc(fit))

filtered_listings_ordered$ID <- seq.int((nrow(filtered_listings_ordered)))


#a line graph is created to obeserve how well the data is predicted. Prices above 10000 are filtered since two values were outliers 

filtered_listings_ordered %>% 
  filter(upr<10000) %>% 
  ggplot(aes(x=ID))+
  geom_line(aes(y=fit,col="Fitted Line"))+
  geom_line(aes(y=price_4_nights,col="Actal Price"))+
  geom_line(aes(y=upr))+
  geom_line(aes(y=lwr))+
  xlab("Observations")+
  ylab("Price for 4 Nights")+
  theme_minimal()



``` 

Utku Odabasi
Chloé Baubier
Jiacheng Zhu
Jay Bensal
Mengtian Li
Yaxin Liu


